Supplementary Material: Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-11-21 si.tex
minor change
a small goof in a figure caption.
final edits

In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
Changing the sign of these parameters can change the sign of $A, B$ and alter the interference between the terms.  
As a specific example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}
	M^{ge}(q) = -1 + 0.04 q,  \\
	\Lambda^{ge}(q) = 0.1 + 0.004 q,
\end{eqnarray}
i.e., $M^{ge}_0 < 0$, $\Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q} > 0$, keeping $\Delta = 0.5$.
Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the destructive interference seen in Figure 3 of the main text.
Similar effects have been recently observed in 1D and 2D coherent resonant Raman experiments.\cite{Fumero2020, Batignani2022}
When the sign of $\Delta$, $M(q)$ and $\Lambda(q)$ match, interference in the output lineshape can be observed.
Changing the absolute sign of these parameters can manipulate the interference (\autoref{fig:chgsign2}).
HDFG therefore has the ability to discern the absolute sign of $\Delta$ and assign offsets in potential energy wells for some systems.

%\newpage
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
	\caption{Contributions of $A, B$ to HDFG spectrum for the simple two harmonic well system described by \autoref{Hamiltonian}, except $M^{ge}(q) = -1 + 0.04 q$.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are scaled to $\max{(A+B)}$. 
} 
	\label{fig:chgsign}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedeltaM.png}
	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 0.01 + 0.004 q$. 
	The respective $\Delta, M^{0}_{ge}$ values are listed above the panels.
	Black trace: $\abs{A+B}$, blue trace: $\abs{A}$, orange trace: $\abs{B}$.
	The spectra are scaled to $\max{\abs{A+B}}$. 
	} 
	\label{fig:chgsign2}
\end{figure}
\newpage
\section{Evaluating the Impact of Static Inhomogeneity on HDFG Spectra}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).

>>>>

In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
Changing the sign of these parameters can change the sign of $A, B$ and alter the interference between the terms.  
As a specific example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}\label{eq:newdipoles}
	M^{ge}(q) = -1 + 0.04 q,  \\
	\Lambda^{ge}(q) = 0.1 + 0.004 q,
\end{eqnarray}
i.e., $M^{ge}_0 < 0$, $\Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q} > 0$, keeping $\Delta = 0.5$.
Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the destructive interference seen in Figure 3 of the main text.
Similar effects have been recently observed in 1D and 2D coherent resonant Raman experiments.\cite{Fumero2020, Batignani2022}
When the sign of $\Delta$, $M(q)$ and $\Lambda(q)$ match, interference in the output lineshape can be observed.
Changing the absolute sign of these parameters can manipulate the interference (\autoref{fig:chgsign2}).
HDFG therefore has the ability to discern the absolute sign of $\Delta$ and assign offsets in potential energy wells for some systems.

%\newpage
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
	\caption{Contributions of $A, B$ to HDFG spectrum for the system described in Figure 3 of the main text, but with $M^{ge}(q)$ described by \autoref{eq:newdipoles}.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are scaled to $\max{(A+B)}$. 
} 
	\label{fig:chgsign}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedeltaM.png}
	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 0.1 + 0.004 q$. 
	The respective $\Delta, M^{0}_{ge}$ values are listed above the panels.
	Black trace: $\abs{A+B}$, blue trace: $\abs{A}$, orange trace: $\abs{B}$.
	The spectra are scaled to $\max{\abs{A+B}}$. 
	} 
	\label{fig:chgsign2}
\end{figure}
\newpage
\section{Evaluating the Impact of Static Inhomogeneity on HDFG Spectra}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
